I knew I was going to die that day. Now, I know this may not sound strange, because there are multiple cases of people knowing they’re going to die. An old person, sitting in their bed, thinking what went wrong and wanting to disappear. And their wish coming true. A person who’s falling from a cliff or a skyscraper, knowing perfectly well they aren’t going to make it. At that moment their life flashes in front of their eyes.

Why was it strange that I knew I was going to die? Because I felt it—a cold breeze as if Death itself was at my window—right before I got to bed at night. And I did, in fact, die in my sleep. Well, actually, I died while I was sleeping. And yes, there’s a difference.

The most peculiar thing is that knowing this crucial fact—the fact that I was going to die that night—I have took no action in preparation. I haven’t said “goodbye” to my friends who were peacefully sleeping in our dorm, or called my family to tell them I loved them. Or, at the very least, called to arrange a funeral. I couldn’t bring myself to do so, because people would either call the ambulance, or just think I’m crazy. Or it would’ve been the two combined.

Now, you would think that since every living person in my dorm was asleep, nobody had noticed my dying. But that’s not the case here. Actually, a whole bunch of people saw my death, a crowd even. And so did Andrew. The boy who followed me around campus, the boy whom I despised. That boy saw me die, held me in his arms when I was almost gone.

During those last few moments I was foolish enough to question myself whether he truly liked me, or, rather, “loved me” like he had told me constantly, on a daily basis.

It may seem like I was selfish for actually concerning myself with the question when he had repeatedly said so.

But you have to hear my side of the story first.