The whole “Andrew story” started quite a long time ago. The first time we had met was the way people usually meet in movies. The same cliché way the creators of teenage shows make the main love interests meet—by colliding into each other in the hallway.

The way it happened was quite simple: I was hurrying along the corridor to my class. As done in the movies, I was carrying a couple of books in my arms—the ones I hadn’t had the chance to stuff into my bag on the way out of my dorm.

The hall was so crowded because normal people come to wait for their classes a little bit earlier than its starting time. I, on the other hand, having my next class way across campus, was running quite late. And I did want to be on time as it was my favorite class out of all of the rest of the selection which I was provided with by my college.

Anyways, there was a group of guys chatting about something unimportant, standing near one of the windows in the massive hallway. And as I neared them, squeezing myself through a group of other students, nearing the windowsills, I hadn’t noticed how one of the tall boys, with his brown curly hair, had stepped out of his “coop”. And right in front of me! I didn’t have enough time to maneuver around him and had collided right into his sturdy shoulder.

The books I was carrying in my hands had spread across the floor. I was this close to doing the same when I felt a hand on my upper arm catch me just in time so I wouldn’t tumble over face first.

Then, I felt myself standing sturdy again, the hand let go and I saw his face. Dark-brown eyes. Dimples.

“Hey, you okay?” his raspy voice asked.

I mumbled something inaudible and then nodded my head. I looked around—nobody seemed to notice my falling. Good.

The boy looked straight into my eyes. Into my soul, even. Eye-contact made me uncomfortable. I put my shoulder-length chestnut hair behind my ear.

He was still looking at me, not letting me bend down to get my scattered books. I must’ve blushed because he let out a soft chuckle, his eyes slipping across my apparently-red cheeks. I moved my hair back onto my face to cover up the embarrassment and the helplessness.

His smile widened for some reason and he finally looked away. Thank God.

He then bent down to pick up the books for me, leaving me to stand awkwardly still in the stream of students, all rushing around me and the boy and his friends who were still standing near the windowsill a little farther back.

When he stood up and handed me the pile of books back with a smile, I wanted to take them and run as fast as I could—with the bell about to ring and all. But he just wouldn’t let me. He was annoying me right from the start!

“Psychology, huh?” he questioned, studying the books’ covers in his hands.

“Yeah…” I answered with a smile as to not be rude to my—apparently—“savior”.

At long last he reached the books to me and I instantly took them—who knows for how long would he be holding them hostage if I hadn’t taken them right away.

“I’m Andrew, by the way,” he smiled, still not letting me get to class.

“April” I answered curtly.

“Cool name,” he said, though it was average.

“Thanks,” I nodded, my chestnut hair coming forward.

He looked at me for a while, me having no idea what that specific look meant.

Then, he as if woke up from a trance.

“You probably need to get to class,” he told me. I was so grateful for his thoughtfulness. I nodded.

“Well, it was nice… you know, meeting you,” he chuckled, “Do I need to make sure you get to class without falling down again?”

“Thanks, I’m good.”

“Alright, see you, April,” he smiled and stepped aside for me to pass. Finally!

I nodded at him again as a form of “thanks” before rushing through the crowd towards my classroom.