We had another "interesting" encounter afterwards.

I was running late again, but this time I wasn't exactly \textit{running} per se. I was still in my dorm, putting my clothes on and trying to pack my books all at once.

And once I dashed out the door, I wished I stayed inside altogether, for the same dark-eyed, brown haired guy was standing right outside!

I knew straight away that he was waiting for me because once he saw me, he started talking. Which was very annoying.

"Hurry up, you're late for class!" he said with a smile.

"What are you doing here?!" I asked.

"I'm here to make sure that you get to the class safely. You know, without falling down," he chuckled.

Amusing.

"Oh, well in that case it's not creepy at all... Andy, was it?" I started saying in an irritated tone.

"It's Andrew."

He sounded disappointed. Why? Because I couldn't remember the name of my "savior"?

"Well, \textit{Andrew}, I've got to get to class, so..."

"That's exactly what I'm here for!"

I had no idea how to respond. What in the world was he talking about? So I continued what I was doing. I started walking along the hallway windows, in the hopes of being only ten minutes late, when he started walking besides me.

"So, which way are you headed?" he asked.

"To my class, obviously."

And I sped up so he'd get the message: I didn't want to walk with him.

Andrew seemed to have noticed my trying to avoid him, so he caught up with me and said:

"Come on, are you being serious right now?"

"What?"

"You don't feel a connection..." he trailed off.

"Between...?"

"You and me!" His eyebrows shot up at my inability to see a connection that never existed.

"What connection are you talking about exactly?"

"April," he spoke solemnly.

"That's she," I answered in a confused manner.
